---
title: "Immigration Report"
author:
- familyname: Dingorkar
  othernames: Priya Ravindra
  address: Monash University
  email: pdin0008@student.monash.edu
  qualifications:  BE in CE & Pursing Master of Business Analytics
  correspondingauthor: true
- familyname: Babu
  othernames: Aarathy
  address: Monash University
  email: abab0012@student.monash.edu
  qualifications:  B.Tech
- familyname: Wang
  othernames: Junhao
  address: Monash University
  email: jwan0296@student.monash.edu
  qualifications: Accounting
- familyname: XXX (Please add your details Dilinie)
  othernames: XXX
  address: XXX
  email: XXX
  qualifications:  XXX
  correspondingauthor: true
department: ETC5513, Group 11\newline Junhao &\newline Aarathy &\newline Dilinie &\newline Priya
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
```


\section*{Research Questions}
  
- Visual summary of corona virus cases and deaths rates in  the following countries
- Please meention about the license part in collab

 \begin{enumerate}
   \item Italia
   \item Germany
 \end{enumerate}

\section*{Introduction}

What is OECD ?

> The Organisation for Economic Co-operation and Development (OECD) is a group of 34 member countries that discuss and develop economic and social policy. OECD members are democratic countries that support free-market economies

What is ISCED ?

>The International Standard Classification of Education is a statistical framework for organizing information on education maintained by the United Nations Educational, Scientific and Cultural Organization. It is a member of the international family of economic and social classifications of the United Nations.

```{r, echo=FALSE, message}
library(readr)
dat <- read_csv("data/DIOC_2015_16_File_D_1.csv")
```

```{r}

```



\section*{Abstract}

\section*{Methodology}

\section*{References}



