---
title: "Immigration Report"
author:
- familyname: Dingorkar
  othernames: Priya Ravindra
  address: Monash University
  email: pdin0008@student.monash.edu
  qualifications:  BE in Computer Enginnering, Pursing Master of Business Analytics
  correspondingauthor: true
- familyname: Babu
  othernames: Aarathy
  address: Monash University
  email: abab0012@student.monash.edu
  qualifications:  B.Tech
- familyname: Wang
  othernames: Junhao
  address: Monash University
  email: jwan0296@student.monash.edu
  qualifications: Accounting
- familyname: Seimon
  othernames: Dilinie
  address: Monash University
  email: asei0003@student.monash.edu
  qualifications:  BSc.
  correspondingauthor: true
department: ETC5513, Group 11\newline Junhao &\newline Aarathy &\newline Dilinie &\newline Priya
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, message=FALSE, warning=FALSE)
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(visdat)
library(scales)
library(gt)
```



\section*{Introduction}

\section*{Abstract}

\section*{Methodology}

\section* {The Education Level of Australian Residents}

```{r reading-data}
fileb1 <- read.csv("data/DIOC_2015_16_File_B_1.csv")
```

```{r cleaning-data}
fileb1cleaned <- fileb1 %>% mutate(
  sex = case_when(
    sex == "1" ~ "male",
    sex == "2"~ "female"
    ),
  edu_lfs = case_when(
    edu_lfs == "1" ~ "low",
    edu_lfs == "2" ~ "medium",
    edu_lfs == "3" ~ "high",
    edu_lfs == "99" ~ "unknown"
  ),
  dos_lfs = case_when(
    dos_lfs == "0" ~ "native-born",
    dos_lfs == "1" ~ "five-years-or-less",
    dos_lfs == "2" ~ "five-to-ten-years",
    dos_lfs == "3" ~ "more-than-ten-years",
    dos_lfs == "23" ~ "more-than-five-years",
    dos_lfs == "99" ~ "unknown",
  ),
  oecd = case_when(
    oecd == "0" ~ "non-member",
    oecd == "1" ~ "member"
  ),
  oecdb = case_when(
    oecdb == "0" ~ "non-member",
    oecdb == "1" ~ "member"
  ),
  fborn = case_when(
    fborn == "0" ~ "native-born",
    fborn == "1" ~ "foreign-born",
    fborn == "99" ~ "unknown"
  )
  )
```

In the past few decades, Australia has acquired many skilled migrants, contributing substantially towards the local economy. @hawthorne2010valuable states that by 2007, two thirds of them were former international students recruited in Australia rather than offshore applicants. This transition has also been named as the "two-step-migration" by @hawthorne2010valuable.

This section will analyse the education levels of current residents of Australia.

The dataset provides information on the education levels of Australian residents and their duration of stay within the country.  
The residents of Australia have been categorized based on their duration of stay within the country as  
- native born  
- less than 5 years  
- between 5 - 10 years  
- more than 10 years  
- unknown  
The level of education has been categorized using a broad three-category classification as  
- low  
- medium  
- high  
- unknown  

```{r summarise-aus-data}
#filter AUS residents
aus_b1 <- fileb1cleaned %>% filter(country == "AUS") %>%
  group_by(dos_lfs,edu_lfs) %>%
  summarise(count = sum(number))
```


```{r tile-plot-edu-vs-duration, fig.cap="Breakdown of Australian residents based on their level of Education and duration of stay in Australia"}
aus_b1 %>% ggplot(aes(x = dos_lfs,
                     y = edu_lfs)) +
  geom_tile(aes(fill = count)) +
  labs(x = "Duration of Stay",
       y = "Level of Education") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c("five-years-or-less", "five-to-ten-years", "more-than-ten-years", "native-born", "unknown")) +
  scale_y_discrete(limits = c("low", "medium", "high", "unknown")) +
  scale_fill_continuous(labels=comma)
```

Figure \@ref(fig:tile-plot-edu-vs-duration) shows the breakdown of Australian residents based on their duration of stay in Australia and their level of education; the higher counts of residents are represented by light blue and the lower number of residents are represented by dark blue. The dataset contains a few unknowns about the Australian resident, some on the level of education and some on the duration of stay, which is also represented in figure \@ref(fig:tile-plot-edu-vs-duration).

It's obvious that the highest counts of Australian residents are natives, and is interesting that a majority of them have a medium level of education, followed by natives having a higher level of education and only a few of them having a low level of education.
It's also interesting how the numbers of Ausralian residents who have been in the country for over ten years, shows higher counts of numbers than those who have been in the country for a lower duration of time. It can also be seen that in all three categories of non-native born Australians, most have received a high level of education.





```{r}
aus_b1_sex <- fileb1cleaned %>% filter(country == "AUS") %>%
  group_by(dos_lfs,edu_lfs, sex) %>%
  summarise(count = sum(number)) %>%
  ungroup() %>%
  pivot_wider(values_from = count,
              names_from = edu_lfs) %>%
  select(dos_lfs, sex, high, medium, low, unknown) %>%
  rename_with(stringr::str_to_title)


aus_b1_sex %>% 
  group_by(Dos_lfs) %>% 
  gt(rowname_col = "Sex") %>% 
  row_group_order(
    groups = c("native-born",
               "more-than-ten-years", 
               "five-to-ten-years", 
               "five-years-or-less",
               "unknown")
            ) %>%
  tab_spanner(label = "Education", 
              columns = matches("High|Low|Medium|Unknown")) %>%
  tab_stubhead(label = "Duration of Stay") %>%
  tab_style(
    style = cell_text(style = "oblique", weight = "bold"),
    locations = cells_row_groups())  %>%
  tab_style(
    style = cell_text(align = "right", style = "italic", weight = "bold"),
    locations = cells_column_labels(
      columns = vars(High, Low, Medium, Unknown)
    ))  %>%
  tab_style(
    style = cell_text(align = "right", weight = "bold"),
    locations = cells_stub())

```


@green2007immigrant states that the immigration policies in Australia has placed an increased focus in skill-based selection criteria, and has resulted in overeducation of recently arrived Australian immigrants. This can be attributed to the most of the recent immigrants having a high level of education as represented by figure \@ref(fig:tile-plot-edu-vs-duration).