---
title: "Immigration Report"
author:
- familyname: Dingorkar
  othernames: Priya Ravindra
  address: Monash University
  email: pdin0008@student.monash.edu
  qualifications:  BE in Computer Enginnering, Pursing Master of Business Analytics
  correspondingauthor: true
- familyname: Babu
  othernames: Aarathy
  address: Monash University
  email: abab0012@student.monash.edu
  qualifications:  B.Tech
- familyname: Wang
  othernames: Junhao
  address: Monash University
  email: jwan0296@student.monash.edu
  qualifications: Accounting
- familyname: Seimon
  othernames: Dilinie
  address: Monash University
  email: asei0003@student.monash.edu
  qualifications:  BSc.
  correspondingauthor: true
department: ETC5513, Group 11\newline Junhao &\newline Aarathy &\newline Dilinie &\newline Priya
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(visdat)
library(scales)
```



\section*{Introduction}

\section*{Abstract}

\section*{Methodology}

\section* {migrants-education}

```{r reading-data}
fileb1 <- read.csv("data/DIOC_2015_16_File_B_1.csv")
```

```{r cleaning-data}
fileb1cleaned <- fileb1 %>% mutate(
  sex = case_when(
    sex == "1" ~ "male",
    sex == "2"~ "female"
    ),
  edu_lfs = case_when(
    edu_lfs == "1" ~ "low",
    edu_lfs == "2" ~ "medium",
    edu_lfs == "3" ~ "high",
    edu_lfs == "99" ~ "unknown"
  ),
  dos_lfs = case_when(
    dos_lfs == "0" ~ "native-born",
    dos_lfs == "1" ~ "five-years-or-less",
    dos_lfs == "2" ~ "five-to-ten-years",
    dos_lfs == "3" ~ "more-than-ten-years",
    dos_lfs == "23" ~ "more-than-five-years",
    dos_lfs == "99" ~ "unknown",
  ),
  oecd = case_when(
    oecd == "0" ~ "non-member",
    oecd == "1" ~ "member"
  ),
  oecdb = case_when(
    oecdb == "0" ~ "non-member",
    oecdb == "1" ~ "member"
  ),
  fborn = case_when(
    fborn == "0" ~ "native-born",
    fborn == "1" ~ "foreign-born",
    fborn == "99" ~ "unknown"
  )
  )
```

In the past few decades, Australia has acquired many skilled migrants, contributing substantially towards the local economy. @hawthorne2010valuable states that by 2007, two thirds of them were former international students recruited in Australia rather than offshore applicants. This transition has also been named as the "two-step-migration" by @hawthorne2010valuable.

Section \@ref(migrants-education) will analyse the education levels of current residents of Australia.

The dataset provides information on the education levels of Australian residents and their duration of stay within the country.  
The residents of Australia have been categorized based on their duration of stay within the country as;
- native born
- less than 5 years
- between 5 - 10 years
- more than 10 years
- unknown
The level of education has been categorized using a broad three-category classification as
- low
- medium
- high
- unknown

```{r summarise-aus-data}
#filter AUS residents
aus_b1 <- fileb1cleaned %>% filter(country == "AUS") %>%
  group_by(dos_lfs,edu_lfs) %>%
  summarise(count = sum(number))
```


```{r tile-plot-edu-vs-duration}
aus_b1 %>% ggplot(aes(x = dos_lfs,
                     y = edu_lfs)) +
  geom_tile(aes(fill = count)) +
  labs(x = "Duration of Stay",
       y = "Level of Education") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(limits = c("five-years-or-less", "five-to-ten-years", "more-than-ten-years", "native-born", "unknown")) +
  scale_y_discrete(limits = c("low", "medium", "high", "unknown")) +
  scale_fill_continuous(labels=comma)
```




